Methods for Large Scale Learning to Rank

### 2014-09-18 report/Chapters/Results.tex
eerste verbeteriteratie

\begin{table}[!h]
\centering
\begin{tabular}{p{3.4cm}p{3.4cm}r}\toprule
Dataset & Collection & Size \\
\midrule
MINI		& GENERATED		  & 143.38 KB\\
OHSUMED     & LETOR 3.0       &   4.55 MB\\
MQ2008      & LETOR 4.0       &   5.93 MB\\
MQ2007      & LETOR 4.0       &  25.52 MB\\
MSLR-WEB10K & MSLR-WEB10K     & 938.01 MB\\
MSLR-WEB30K & MSLR-WEB30K     &   2.62 GB\\
CUSTOM-2	& GENERATED		  &   5.25 GB\\
CUSTOM-5	& GENERATED		  &  13.12 GB\\
CUSTOM-10	& GENERATED		  &  26.24 GB\\
CUSTOM-20   & GENERATED       &  52.42 GB\\
CUSTOM-50	& GENERATED		  & 131.21 GB\\
CUSTOM-100	& GENERATED		  & 262.41 GB\\
\bottomrule
\end{tabular}
\caption{Description of datasets used for running time experiments}
\label{tbl:recap_datasets}
\end{table}

Figures \ref{fig:listnet_train_time} and \ref{fig:listnet_train_time_log} show that the single-machine RankLib implementation of ListNet is very fast compared to the Hadoop MapReduce cluster implementation of ListNet for datasets that fit in memory. As soon as the amount of data processed with RankLib ListNet approaches the physical memory limit of the machine used for the computation (16 GB for the machine used in our experiments), RankLib ListNet processing time start to increase very rapidly. This increase is likely to be a result of swapping data to and from virtual memory. The largest dataset processed with RankLib ListNet is CUSTOM-8, which is 20.99 GB in size and therewith larger than the 16 GB physical memory limit. Experiments with RankLib ListNet on CUSTOM-10 were attempted, but were stopped after not completing within 12 hours.\\

@@

Figure \ref{fig:speedup_train_time} shows that speed-up is sub-linear such that the training time converges to a constant unit of time somewhere within the range of 150-200 seconds. This time is likely to be caused by Hadoop job scheduling overhead, this presumption is strengthened by long waiting periods between the separate MapReduce jobs that form a training iteration.\\

Amdahl's law states that the speed-up of a program using parallel computing is limited by the time needed for the sequential fraction of the program. A consequence of Amdahl's Law is that all parallel programs the have a non-parallelisable part have sub-linear speed-up. Behaviour in accordance with Amdahl's law can be seen in Figure \ref{fig:speedup_train_time}, where the speed-up is sub-linear as a result of the existence a non-parallelisable fraction of the program.\\

>>>>

\begin{table}[!h]
\centering
\begin{tabular}{p{3.4cm}p{3.4cm}r}\toprule
Dataset & Collection & Single fold training size \\
\midrule
MINI		& GENERATED		  & 143.38 KB\\
OHSUMED     & LETOR 3.0       &   4.55 MB\\
MQ2008      & LETOR 4.0       &   5.93 MB\\
MQ2007      & LETOR 4.0       &  25.52 MB\\
MSLR-WEB10K & MSLR-WEB10K     & 938.01 MB\\
MSLR-WEB30K & MSLR-WEB30K     &   2.62 GB\\
CUSTOM-2	& GENERATED		  &   5.25 GB\\
CUSTOM-5	& GENERATED		  &  13.12 GB\\
CUSTOM-10	& GENERATED		  &  26.24 GB\\
CUSTOM-20   & GENERATED       &  52.42 GB\\
CUSTOM-50	& GENERATED		  & 131.21 GB\\
CUSTOM-100	& GENERATED		  & 262.41 GB\\
\bottomrule
\end{tabular}
\caption{Description of datasets used for running time experiments}
\label{tbl:recap_datasets}
\end{table}

Figures \ref{fig:listnet_train_time} and \ref{fig:listnet_train_time_log} show that the single-machine RankLib implementation of ListNet is very fast compared to the Hadoop MapReduce cluster implementation of ListNet for datasets that fit in memory. As soon as the amount of data processed with RankLib ListNet approaches the physical memory limit of the machine that is used for computation (16 GB for our single-machine measurements), RankLib ListNet processing time start to increase exponentially. This increase is likely to be a result of the machine needing to use the on-disk sections of virtual memory and the swapping that takes place as a result thereof. As an exception to the datasets described in Table \ref{tbl:recap_datasets}, the largest dataset processed with RankLib ListNet is CUSTOM-8, which is 20.99 GB in size and thereby larger than the 16 GB physical memory limit. Experiments with RankLib ListNet on CUSTOM-10 were attempted, but were stopped after not completing within 12 hours. In section \ref{sec:goals} we defined speed-up as Sun and Gustafson \emph{relative speed-up} metric \cite{Sun1991} (as stated in section \ref{sec:goals}), which defines speed-up as the number of times that the execution of the fastest single machine solution is lower than the execution time with $N$ machines. Note that speed-up, following this definition, is not computable for larger datasets, as it is not computationally feasible to perform computation on datasets larger than CUSTOM-8 with a single machine. As an alternative, Figure \ref{fig:speedup_train_time} shows visualises speed-up by plotting cluster size against training time.\\

@@

Figure \ref{fig:speedup_train_time} shows that speed-up is sub-linear, from which we can deduct that the training time converges to a constant unit of time. Based on our measurements on the small datasets MINI, OHSUMED, MQ2008 and MQ2007, this constant time seems to be within the range of 150 to 200 seconds. This time is likely to be caused by Hadoop job scheduling overhead, this presumption is strengthened by long waiting periods between the separate MapReduce jobs that form a training iteration.\\

Amdahl's law states that the speed-up of a program using parallel computing is limited by the time needed for the sequential fraction of the program. A consequence of Amdahl's Law is that all parallel programs that have a non-parallelisable part have sub-linear speed-up. Behaviour in accordance with Amdahl's law can be seen in Figure \ref{fig:speedup_train_time}, where the speed-up is sub-linear as a result of the existence a non-parallelisable fraction of the program.\\
